---
title: "Phishing Study ICITDA 2021"
author: "Ahmad R Pratama"
date: "7/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r, warning=FALSE, message=FALSE}
library(psych)
library(tidyverse)
library(printr)
library(ggpubr)
library(car)
library(summarytools)
library(emmeans)
library(rstatix)
library(ggiraphExtra)
```

# Attach dataset
```{r, warning=FALSE, message=FALSE}
data <- read_csv("phishingdataset247.csv")
data <- data[, c('id', 'gender', 'age','agegroup', 'group', 'score', 'literacy','agelit')]
head(data)
summary(data)
```
## Descriptive statistics
```{r}
freq(data, report.nas = F)
descr(data$score)
hist(data$score)
descr(data$age)
hist(data$age)
descr(data$literacy)
hist(data$literacy)
descr(data$agelit)
hist(data$agelit)
tapply(data$score, data$gender, summary)
tapply(data$score, data$agegroup, summary)
tapply(data$score, data$group, summary)
```
# Checking Assumptions
## Linearity
```{r}
ggscatter(
  data, x = "literacy", y = "score",
  facet.by  = c("gender", "group"), 
  short.panel.labs = FALSE
  )+
  stat_smooth(method = "loess", span = 0.9)

ggscatter(
  data, x = "age", y = "score",
  facet.by  = c("gender", "group"), 
  short.panel.labs = FALSE
  )+
  stat_smooth(method = "loess", span = 0.9)

ggscatter(
  data, x = "agelit", y = "score",
  facet.by  = c("gender", "group"), 
  short.panel.labs = FALSE
  )+
  stat_smooth(method = "loess", span = 0.9)
```
## Homogeneity of regression slopes
```{r}
res.aov <- data %>%
  anova_test(
    score ~ age + gender + group + 
     group*gender + age*group +
     age*gender + age*gender*group
  )
get_anova_table(res.aov)

res.aov <- data %>%
  anova_test(
    score ~ literacy + gender + group + 
     group*gender + literacy*group +
     literacy*gender + literacy*gender*group
  )
get_anova_table(res.aov)

res.aov <- data %>%
  anova_test(
    score ~ agelit + gender + group + 
     group*gender + agelit*group +
     agelit*gender + agelit*gender*group
  )
get_anova_table(res.aov)
```
## Compute mean and SD
```{r}
data %>%
  group_by(gender, group) %>%
  get_summary_stats(score, type = "mean_sd")

data %>%
  group_by(gender) %>%
  get_summary_stats(score, type = "mean_sd")

data %>%
  group_by(group) %>%
  get_summary_stats(score, type = "mean_sd")

data %>%
  group_by(agegroup) %>%
  get_summary_stats(score, type = "mean_sd")

data %>%
  get_summary_stats(score, type = "mean_sd")
```
## Normality assumption
```{r}
model1  <- lm(score ~ literacy+gender*group, data = data)
# Create a QQ plot of residuals
ggqqplot(residuals(model1))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model1))

model2  <- lm(score ~ age+gender*group, data = data)
# Create a QQ plot of residuals
ggqqplot(residuals(model2))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model2))

model3  <- lm(score ~ agelit+gender*group, data = data)
# Create a QQ plot of residuals
ggqqplot(residuals(model3))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model3))
```
## Homogneity of variance assumption
```{r}
data %>% levene_test(score ~ gender*group)
```
# ANCOVA Computation
```{r}
mod <- lm(score ~ group*gender, data=data)
Anova(mod)
```
```{r}
res.aov <- data %>% 
  anova_test(score ~ group*gender)
get_anova_table(res.aov)
```
```{r}
res1<-Anova(lm(score ~ group*gender, data=data))
anova_summary(res1, detailed = T)
```
```{r}
mod <- lm(score ~ age+group*gender, data=data)
Anova(mod)
```

```{r}
res.aov3 <- data %>% 
  anova_test(score ~ agegroup*group*gender, effect.size = "both")
get_anova_table(res.aov3)
```
```{r}
res2<-Anova(lm(score ~ age+group*gender, data=data, type=2))
anova_summary(res2, detailed = T)
```
```{r}
res2<-Anova(lm(score ~ agegroup*group*gender, data=data, type=2))
anova_summary(res2, detailed = T)
```
```{r}
res.aov2 <- data %>% 
  anova_test(score ~ literacy+group*gender)
get_anova_table(res.aov2)

res.aov4 <- data %>% 
  anova_test(score ~ agelit+group*gender)
get_anova_table(res.aov4)
```
## Output Table
```{r}
#anova(lm(score ~ agelit+group*gender, data=data))
library(apaTables)
lm_output<-(lm(score ~ group*gender, data=data, type=2))
apa.aov.table(lm_output, filename = "Table1_APA.doc", table.number = 1)

lm_output<-(lm(score ~ age+group*gender, data=data, type=2))
apa.aov.table(lm_output, filename = "Table1_APA.doc", table.number = 1)
```

## Multiple pairwise comparisons
```{r}
pwc <- data %>%
  group_by(gender) %>%
  emmeans_test(score ~ group, p.adjust.method = "bonferroni") %>%
  select(-df, -statistic, -p)
pwc
get_emmeans(pwc)
```
# Visualization
## Boxplots
```{r}

bxp <- ggboxplot(
  data, x = "group", y = "score", 
  color = "gender", palette = "lancet", 
  xlab = "Intervention", ylab = "Phishing Awareness Score"
  )
bxp

pwc <- pwc %>% add_xy_position(x = "group")
bxp +
  stat_pvalue_manual(
    pwc, color = "gender", hide.ns = TRUE,
    tip.length = 0, step.increase = 0.1, 
  ) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

pwc <- pwc %>% add_xy_position(x = "group")
bxp +
  stat_pvalue_manual(
    pwc, color = "gender", hide.ns = TRUE,
    tip.length = 0, step.increase = 0.1, 
  ) +
  labs(
    subtitle = get_test_label(res.aov2, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

pwc <- pwc %>% add_xy_position(x = "group")
bxp +
  stat_pvalue_manual(
    pwc, color = "gender", hide.ns = TRUE,
    tip.length = 0, step.increase = 0.1, 
  ) +
  labs(
    subtitle = get_test_label(res.aov3, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

pwc <- pwc %>% add_xy_position(x = "group")
bxp +
  stat_pvalue_manual(
    pwc, color = "gender", hide.ns = TRUE,
    tip.length = 0, step.increase = 0.1, 
  ) +
  labs(
    subtitle = get_test_label(res.aov4, detailed = TRUE),
    caption = get_pwc_label(pwc)
    )

```

## Scatterplots
```{r}
fit1 = lm(score~age+group*gender, data=data)
summary(fit1)
ggPredict(fit1,se=F,interactive=F)
```


```{r}
fit2 = lm(score~literacy+group*gender, data=data)
summary(fit2)
ggPredict(fit2,se=F,interactive=F)

fit3 = lm(score~agelit+group*gender, data=data)
summary(fit3)
ggPredict(fit3,se=F,interactive=F)
```
# Three-Way ANOVA
```{r}
data %>%
  group_by(agegroup, gender, group) %>%
  get_summary_stats(score, type = "mean_sd")
```
## Boxplot
```{r}
bxp3 <- ggboxplot(
  data, x = "group", y = "score", 
  color = "agegroup", palette = "lancet", facet.by = "gender", 
  ylab = "Phishing Awareness Score", xlab = "Intervention"
  )
bxp3
```
## Outliers
```{r}
data %>%
  group_by(agegroup, gender, group) %>%
  identify_outliers(score)
```
## Normality assumption
```{r}
model  <- lm(score ~ agegroup*gender*group, data = data)
# Create a QQ plot of residuals
ggqqplot(residuals(model))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model))
```
## Homogneity of variance assumption
```{r}
data %>% levene_test(score ~ agegroup*gender*group)
```
## Computation
```{r}
res.aov <- data %>% anova_test(score ~ agegroup*gender*group)
res.aov
mod <- lm(score ~ agegroup*group*gender, data=data)
Anova(mod, type=2)
```
## Post-hoc Test
```{r}
model  <- lm(score ~ agegroup*gender*group, data = data)
data %>%
  group_by(gender) %>%
  anova_test(score ~ agegroup*group, error = model)
```
## Pairwise Comparison
```{r}
# Pairwise comparisons
library(emmeans)
pwc3 <- data %>%
  group_by(agegroup, gender) %>%
  emmeans_test(score ~ group, p.adjust.method = "bonferroni") %>%
  select(-df, -statistic, -p) # Remove details
# Show comparison results for male at high risk
pwc3
pwc3 %>% filter(agegroup == "1.teens", gender == "male")
```

## Visualization
```{r}
# Visualization: box plots with p-values
pwc3 <- pwc3 %>% add_xy_position(x = "group")
pwc.filtered <- pwc3 %>% filter(agegroup == "1.teens", gender == "male")
bxp3 +
  stat_pvalue_manual(
    pwc.filtered, color = "agegroup", linetype = "agegroup", hide.ns = TRUE,
    tip.length = 0, step.increase = 0.1, step.group.by = "gender"
  ) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc), ylab="Phishing Awareness Score"
    )
```

